---
title: "Training Report"
author: "Georgia Scott"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2)
library(dplyr)
library(plotly)
library(htmlwidgets)
library(hms)
library(readxl)
library(condformat)


round_mean <- function(x) {
  round(mean(x), digits = 0) 
}

round_mean2 <- function(x) {
  round(mean(x), digits = 1)  
}

setwd("DataLocation")
datadump<-suppressWarnings(read_xlsx("GPS - Database - Heart Rate.xlsx",sheet=1)) ### gps file
#datadump<-subset(datadump,datadump$Season=="2025/26") #option to only look at this season drills or all of time
sched<-read.csv("Schedule.csv") ## schedule to know what day type you have 
sched$active_days<- as.Date(sched$active_days, format = "%d/%m/%Y")
datadump$`Total Time`<-as.numeric(as_hms(datadump$`Total Time`))/60
datadump$`Session Date`<-as.Date(datadump$`Session Date`)
datadump$`Total Distance`<-round(datadump$`Total Distance`,digits=0)
datadump$`Player Position` <- factor(datadump$`Player Position`, levels = c("Prop","Hooker","Second Row","Back Row","Scrum Half","Out Half","Centre","Back Three"))

### tidy up position groups and metric names if required. 
datadump$PositionGroup<-ifelse(datadump$`Player Position` %in% c("Prop","Hooker","Back Row","Second Row"),"Forward","Back")
colnames(datadump)[colnames(datadump) == "Total Distance"] <- "Total Distance"
colnames(datadump)[colnames(datadump) == "Player Name"] <- "Name"
colnames(datadump)[colnames(datadump) == "HML Distance"] <- "HMLD"
colnames(datadump)[colnames(datadump) == "Position"] <- "Position2"
colnames(datadump)[colnames(datadump) == "Player Position"] <- "Position"
colnames(datadump)[colnames(datadump) == "High Speed Running (Relative)"] <- "VHSR >70%"
colnames(datadump)[colnames(datadump) == "Accelerations"] <- "Accels"
colnames(datadump)[colnames(datadump) == "% Accel GD"] <- "Accels old"
colnames(datadump)[colnames(datadump) == "Accels GD"] <- "Accels old2"
colnames(datadump)[colnames(datadump) == "VHSR GD"] <- "VHSR old2"
colnames(datadump)[colnames(datadump) == "% VHSR GD"] <- "VHSR old"


datadump$MMin<-round(datadump$`Total Distance`/datadump$`Total Time`,digits=1)
datadump$HMLMin<-round(datadump$`HMLD`/datadump$`Total Time`,digits=1)
datadump$AccelMin<-round(datadump$Accels/datadump$`Total Time`,digits=1)
datadump$VHSRMin<-round(datadump$`VHSR >70%`/datadump$`Total Time`,digits=1)
datadump$Initials <- sapply(strsplit(datadump$Name, " "), function(x) paste0(substr(x, 1, 1), collapse = ""))
datadump$`VHSR >70%`<-round(datadump$`VHSR >70%`,digits=0)
datadump$HMLD<-round(datadump$HMLD,digits=0)
datadump<-subset(datadump,datadump$`Session Date`>"2024-07-28")
datadump <- merge(datadump, sched, by.x = "Session Date", by.y = "active_days", all.x = TRUE)
#training<-subset(datadump,grepl("2026-01-15",datadump$`Session Date`)) # if analysing in day after training
training<-subset(datadump,grepl(Sys.Date(),datadump$`Session Date`))

trainingfull<-subset(training,training$`Drill Title`=="Rugby - Team - Session & Units") ## example of selected part of session


```

## Week Summary
```{r, echo=FALSE,message=FALSE,warning=FALSE, out.width="125%",out.height="125%"}
target_week <- unique(datadump$`Session Week Number`[datadump$`Session Date` == Sys.Date()])
if (length(target_week) == 1) {
  week <- datadump[datadump$`Session Week Number` == target_week, ]
} else {
  warning("Date matched multiple or no week numbers.")
}
weekfull<-subset(week,`Drill Title`=="Rugby - Team - Session & Units"|`Drill Title`=="Rugby - Team - Session & Units")
weekfull<-subset(weekfull,weekfull$Season=="2025/26")
rowsum <- weekfull %>%
  group_by(Name) %>%
  dplyr::summarize(PositionGroup=PositionGroup,
                   HMLD=round(sum(HMLD,na.rm=TRUE),digit=0),
                    Accels=round(sum(Accels,na.rm=TRUE),digit=0),
                    `VHSR >70%`=round(sum(`VHSR >70%`,na.rm=TRUE),digit=0))

rowdata <- rowsum %>%
  group_by(PositionGroup) %>%
  dplyr::summarize(HMLD=round(mean(HMLD,na.rm=TRUE),digit=0),
                    Accels=round(mean(Accels,na.rm=TRUE),digit=0),
                    `VHSR >70%`=round(mean(`VHSR >70%`,na.rm=TRUE),digit=0))


my.data <- as.data.frame(rowdata)

colnames(rowdata)[1]<-"Position"
tablestats<-rowdata

tablestats$Position<-as.factor(tablestats$Position)
my.data <- as.data.frame(tablestats)

color.picker1 <- function(z){
  if(is.na(z)){return(0)}
  else if(z <= 5){return(1)}
  else if( z > 5 & z < 15){return(2)}
  else {return(3)}
}
color.picker2 <- function(z){
  if(is.na(z)){return(0)}
  else if(z <= 0.5){return(1)}
  else if( z > 1 & z < 2){return(2)}
  else {return(3)}
}
color.picker3 <- function(z){
  if(is.na(z)){return(0)}
  else if(z <= 0){return(1)}
  else if( z > 1 & z < 5){return(2)}
  else {return(3)}
}

a<-condformat(my.data) %>%
  rule_fill_discrete(HMLD, expression = sapply(HMLD,
                                                color.picker1),colours=c("0" = "white", "1" = "red", 
                                                                          "2" =  "yellow", "3" = "lightgreen"))
b<-a %>%rule_fill_discrete(`VHSR >70%`, expression = sapply(`VHSR >70%`,
                                                          color.picker3),colours=c("0" = "white", "1" = "red", 
                                                                                   "2" =  "yellow", "3" = "lightgreen")) 
c<-b %>%
  rule_fill_discrete(Accels, expression = sapply(Accels,
                                                      color.picker2),colours=c("0" = "white", "1" = "red",  "2" =  "yellow", "3" = "lightgreen")) 

c

```

## Session Summary

```{r, echo=FALSE,message=FALSE,warning=FALSE, out.width="125%",out.height="125%"}
rowdata <- trainingfull %>%
  group_by(PositionGroup) %>%
  dplyr::summarize(HMLD=round(mean(HMLD,na.rm=TRUE),digit=0),
                    Accels=round(mean(Accels,na.rm=TRUE),digit=0),
                    `VHSR >70%`=round(mean(`VHSR >70%`,na.rm=TRUE),digit=0))

my.data <- as.data.frame(rowdata)

daydata<-subset(datadump,datadump$day_type==trainingfull$day_type & datadump$`Drill Title`=="Rugby - Team - Session & Units")
dayreference <- daydata %>%
  group_by(PositionGroup) %>%
  dplyr::summarize(HMLDnorm=round(mean(HMLD,na.rm=TRUE),digit=0),
                    Accelsnorm=round(mean(Accels,na.rm=TRUE),digit=0),
                    VHSRnorm=round(mean(`VHSR >70%`,na.rm=TRUE),digit=0))

my.data<-cbind(my.data,dayreference[,c(2:4)])
my.data$HMLDPercent<-100*round(my.data$HMLD/my.data$HMLDnorm,digit=2)
my.data$AccelPercent<-100*round(my.data$Accels/my.data$Accelsnorm,digit=2)
my.data$VHSRPercent<-100*round(my.data$`VHSR >70%`/my.data$VHSRnorm,digit=2)

color.picker1 <- function(z){
  if(is.na(z)){return(0)}
  else if(z <= 80){return(1)}
  else if( z > 80 & z < 120){return(2)}
  else {return(3)}
}

a<-condformat(my.data) %>%
  rule_fill_discrete(HMLD, expression = sapply(my.data$HMLDPercent,
                                                color.picker1),colours=c("0" = "white", "1" = "navy", 
                                                                          "2" =  "lightgreen", "3" = "darkred"))

b<-a %>%rule_fill_discrete(`VHSR >70%`, expression = sapply(my.data$VHSRPercent,
                                                          color.picker1),colours=c("0" = "white", "1" = "navy", 
                                                                                   "2" =  "lightgreen", "3" = "darkred")) 

c<-b %>%
  rule_fill_discrete(Accels, expression = sapply(my.data$AccelPercent,
                                                      color.picker1),colours=c("0" = "white", "1" = "navy",  "2" =  "lightgreen", "3" = "darkred")) 

c[,c(1:4)]
```

# Session Versus Game - Volume
Comparison to average game for the position group, volume is based on playing over 65 minutes. 

Colour code - <80% blue, 80-120% green 120%+ red
```{r, echo=FALSE,message=FALSE,warning=FALSE, out.width="125%",out.height="125%"}
#### session versus game ####
#### session versus game ####

match <- subset(datadump,
                grepl("Match - 1st Half", datadump$`Drill Title`, ignore.case = TRUE) |
                grepl("Match - 2nd Half", datadump$`Drill Title`, ignore.case = TRUE))

matchsum <- match %>%
  group_by(Name, `Session Date`) %>%
  dplyr::summarise(
    Position = Position,
    `Total Distance`=sum(`Total Distance`),
    HMLD = sum(HMLD),
    Accels = sum(Accels),
    `VHSR >70%` =sum(`VHSR >70%`),
    MMin = mean(MMin),
    HMLMin = mean(HMLMin),
    AccelMin = mean(AccelMin),
    VHSRMin = mean(VHSRMin),
    total_time = sum(`Total Time`)
  )

matchsum <- matchsum[!duplicated(matchsum),]

matchsum <- subset(matchsum, matchsum$total_time > 65)

ma <- matchsum %>%
  group_by(Position) %>%
  dplyr::summarise(
    across(c(`HMLMin`,`AccelMin`,`VHSRMin`,`HMLD`,`Accels`, `VHSR >70%`), mean, na.rm = TRUE)
  )

colnames(ma)[2:7] <- paste(colnames(ma)[2:7], "GD")

trainingteam <- subset(training, training$`Drill Title` == "Rugby - Team - Session & Units")

sgame <- merge(trainingteam, ma, by = "Position")

### repeat for volume ###

sgame$`% HMLD GD`<- round(100 * (sgame$HMLD / sgame$`HMLD GD`), digits = 0)
sgame$`% Accel GD` <- round(100 * (sgame$Accels / sgame$`Accels GD`), digits = 0)
sgame$`VHSR GD` <- round(100 * (sgame$`VHSR >70%` / sgame$`VHSR >70% GD`), digits = 0)

metricnumber3 <- c(202,203,204)## position in table of metrics, this can changed to index of the metric name if prefered
metricnumber3 <- as.data.frame(metricnumber3)
metricnumber3$MetricName <- c("% HMLD GD","% Accel GD","% VHSR GD")

plot_list3 <- list()

# Iterate over each metric
for (col in metricnumber3[, 1]) {

  metric_name <- metricnumber3$MetricName[metricnumber3$metricnumber3 == i]

  # Calculate mean and standard deviation for each PositionGroup
  summary_stats <- sgame %>%
    group_by(Position) %>%
    dplyr::summarize(
      Mean = round(mean(.data[[colnames(sgame)[col]]], na.rm = TRUE), digits = 0),
      sd = sd(.data[[colnames(sgame)[col]]], na.rm = TRUE)
    )

  means <- sgame %>%
    group_by(PositionGroup) %>%
    dplyr::summarize(
      Mean = round(mean(.data[[colnames(sgame)[col]]], na.rm = TRUE), digits = 0)
    )

  forward <- subset(means, PositionGroup == "Forward")
  back <- subset(means, PositionGroup == "Back")

  colnames(back)[2] <- "Backs Mean"
  colnames(forward)[2] <- "Forwards Mean"

  max_abs <- max(abs(c(min(sgame[[names(sgame)[col]]]), max(sgame[[names(sgame)[col]]]))))

  summary_stats$fill_color <- ifelse(summary_stats$Mean < 80,
                                     "navy",
                                     ifelse(summary_stats$Mean >= 80 & summary_stats$Mean < 120,
                                            "lightgreen",
                                            "darkred"))

  a <- ggplot(data = sgame,
              aes(x = Position,
                  y = .data[[names(sgame)[col]]])) +

    geom_bar(stat = "summary",
             position = "dodge",
             fun = round_mean,
             fill = summary_stats$fill_color) +

    geom_text(aes(label = Initials,
                  color = as.factor(Name),
                  Name = Name),
              vjust = -0.5) +

    xlab("") +

    scale_color_manual(labels = c("My Line 1", "My Line 2"),
                       values = c("Line 1" = "blue", "Line 2" = "red")) +

    ylab(paste(metric_name)) +

    scale_y_continuous(labels = function(x) paste0(x, "%")) +

    theme(
      legend.title = element_blank(),
      axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1),
      text = element_text(size = 16)
    )

  b <- ggplotly(a,
                tooltip = c("Mean","Name","Position","Forwards Mean","Backs Mean", paste(colnames(sgame)[i]))) %>%
    layout(
      legend = list(title = NULL),
      hovermode = "closest",
      hoverlabel = list(font = list(color = "white")),
      pointmeta = list(text = paste(colnames(sgame)[i]))
    )

  plot_list3[[length(plot_list3) + 1]] <- b
}

# Combine the plots into a single Plotly object

combined_plotsg <- subplot(plot_list3,
                           nrows = 1,
                           shareX = FALSE,
                           shareY = FALSE,
                           titleY = TRUE,
                           margin = 0.05)

# Customize legend settings

combined_plotsg <- combined_plotsg %>%
  layout(
    legend = list(
      traceorder = "normal",
      font = list(color = "black"),
      bgcolor = "white",
      bordercolor = "white",
      borderwidth = 1
    )
  )

# Display the combined plot for session compared to game

combined_plotsg

```
# Session Versus Game - Intensity

Colour coded based on average game, intensity is based on 40 minute half.
<80% Blue 
80-120% Green
120%+ Red

```{r, echo=FALSE,message=FALSE,warning=FALSE, out.width="125%",out.height="125%"}
matchfirsthalf<-subset(datadump,grepl("Match - 1st Half",datadump$`Drill Title`))
matchfirsthalf<-subset(matchfirsthalf,matchfirsthalf$`Total Time`>40)
matchsum<-matchfirsthalf %>%
  group_by(Name,`Session Date`) %>%
  dplyr::summarise(Position=Position,
                   `Total Distance`=sum(`Total Distance`),
                   HMLD=sum(HMLD),
                   Accels =sum(Accels),
                   `VHSR >70%` =sum(`VHSR >70%`),
                   MMin=mean(MMin),
                   HMLMin=mean(HMLMin),
                   AccelMin=mean(AccelMin),
                   VHSRMin=mean(VHSRMin),
                   total_time=sum(`Total Time`))


ma <- matchsum %>%
  group_by(`Position`) %>%
  dplyr::summarise(across(c("HMLMin","AccelMin","VHSRMin","HMLD","Accels",`VHSR >70%`),mean,na.rm=TRUE))

colnames(ma)[2:7]<-paste(colnames(ma)[2:7],"GD")

trainingteam<-subset(training,training$`Drill Title`=="Rugby - Team - Session & Units")

sgame<-merge(trainingteam,ma,by= "Position")


sgame$"% HMLD/Min GD"<-round(100*(sgame$HMLMin/sgame$`HMLMin GD`)-100,digits=0)
sgame$"% Accel/Min GD"<-round(100*(sgame$AccelMin/sgame$`AccelMin GD`)-100,digits=0)
sgame$"% VHSR/Min GD"<-round(100*(sgame$VHSRMin/sgame$`VHSRMin GD`)-100,digits=0)

#sgame$fill_color <- ifelse(summary_stats$mean < 0, "navy", "darkred")

metricnumber3<-c(202,203,204)## position in table of metrics, this can changed to index of the metric name if prefered
metricnumber3<-as.data.frame(metricnumber3)
metricnumber3$MetricName<-c("% HMLD/Min GD","% Accel/Min GD","% VHSR/Min GD")

plot_list3 <- list()

# Iterate over each metric
for (i in metricnumber3[, 1]) {
  metric_name <- metricnumber3$MetricName[metricnumber3$metricnumber3 == i]  
  
  # Calculate mean and standard deviation for each PositionGroup
  summary_stats <- sgame %>%
    group_by(Position) %>%
    dplyr::summarize(Mean = round(mean(.data[[colnames(sgame)[i]]], na.rm = TRUE),digits=0),
              sd = sd(.data[[colnames(sgame)[i]]], na.rm = TRUE))
  means<-sgame %>%
    group_by(PositionGroup)%>%
    dplyr::summarize(Mean=round(mean(.data[[colnames(sgame)[i]]],na.rm=TRUE),digits = 0))
  forward <- subset(means, PositionGroup == "Forward")
  back <- subset(means, PositionGroup == "Back")
  colnames(back)[2]<-"Backs Mean"
  colnames(forward)[2]<-"Forwards Mean"
  max_abs <- max(abs(c(min(sgame[[names(sgame)[i]]]), max(sgame[[names(sgame)[i]]]))))
  summary_stats$fill_color <- ifelse(summary_stats$Mean <= -20, "navy",ifelse(summary_stats$Mean>-20 & summary_stats$Mean<20,"lightgreen", "darkred"))
  a <- ggplot(data = sgame, aes(x = Position, y = .data[[names(sgame)[i]]])) +
    geom_bar(stat = "summary", position = "dodge", fun = round_mean,fill=summary_stats$fill_color) +
    geom_text(aes(label = Initials, color=as.factor(Name),Name=Name),  
              vjust = -0.5) +
   # geom_hline(data = forward, aes(yintercept = `Forwards Mean`), 
    #           color = "orange", linetype = "dashed", linewidth = 1) +
    #geom_hline(data = back, aes(yintercept = `Backs Mean`), 
     #          color = "green", linetype = "dashed", linewidth = 1) +
    xlab("") +
    scale_color_manual(labels = c("My Line 1", "My Line 2"),
                       values = c("Line 1" = "blue", "Line 2" = "red"))+
    ylab(paste(metric_name)) +
    scale_y_continuous(labels = function(x) paste0(x, "%"),limits=c(-max_abs, max_abs))+
    theme(
      legend.title = element_blank(),
      axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1),
      text = element_text(size = 16)
    )
  
  b <- ggplotly(a, tooltip = c("Mean","Name", "Position","Forwards Mean", "Backs Mean", paste(colnames(sgame)[i])),visible=legendonly) %>%
    layout(legend = list(title = NULL),
           hovermode = "closest",
           hoverlabel = list(font = list(color = "white")),
           pointmeta = list(text = paste(colnames(sgame)[i])))
  #b$x$data[[2]]$hoverinfo <- "none"
  
  plot_list3[[length(plot_list3) + 1]] <- b
}

# Combine the plots into a single Plotly object
combined_plotsg <- subplot(plot_list3, nrows=1, shareX = FALSE, shareY = FALSE,titleY = TRUE,margin=0.05)

# Customize legend settings
combined_plotsg <- combined_plotsg %>% layout(
  legend = list(
    traceorder = "normal",  # Ensure the order of legend items is consistent
    font = list(color = "black"),  # Customize legend font color
    bgcolor = "white",  # Set legend background color
    bordercolor = "white",  # Set legend border color
    borderwidth = 1  # Set legend border width
  )
)

# Display the combined plot for session compared to game 
combined_plotsg

```
# Drill Report

Colour coded based on drill in previous sessions, only within the current season.
<80% Blue 
80-120% Green
120%+ Red

```{r, echo=FALSE,message=FALSE,warning=FALSE, out.width="125%",out.height="125%"}
exclude_words <- c("Prep", "Extras", "Full Session","Session & Units","Units","Rehab","Cond","Craft") # to avoid naming drills, you can exclude words here
trainingdrills <- training[!grepl(paste(exclude_words, collapse="|"), training$`Drill Title`), ]
trainingdrills$`Drill Title` <- factor(
  trainingdrills$`Drill Title`,
  levels = unique(
    trainingdrills$`Drill Title`[
      order(trainingdrills$`Drill Start Time`)
    ]
  )
)
drill_order <- unique(
  trainingdrills$`Drill Title`[
    order(trainingdrills$`Drill Start Time`)
  ]
)
metricnumber2<-c(188,189,190) ## position in table of metrics, this can changed to index of the metric name if prefered
metricnumber2<-as.data.frame(metricnumber2)
metricnumber2$MetricName<-c("Av.HMLD/Min","Av.Accel/Min","Av.VHSR/Min")
metricnumber2$value<-c(10,1,1)
### make a nice table first 
tablestats <- trainingdrills %>%
  group_by(`Drill Title`) %>%
  dplyr::summarize( HMLMin=round(mean(HMLMin,na.rm=TRUE),digit=1),
                    AccelMin=round(mean(AccelMin,na.rm=TRUE),digit=1),
                    VHSRMin=round(mean(VHSRMin,na.rm=TRUE),digit=1))

tablestats$`Drill Title`<-as.factor(tablestats$`Drill Title`)
my.data <- as.data.frame(tablestats)

drilldata<-subset(datadump,datadump$`Drill Title` %in%trainingdrills$`Drill Title`)
dayreference <- drilldata %>%
  group_by(`Drill Title`) %>%
  dplyr::summarize(HMLDnorm=round(mean(HMLMin,na.rm=TRUE),digit=1),
                    Accelsnorm=round(mean(AccelMin,na.rm=TRUE),digit=1),
                    VHSRnorm=round(mean(VHSRMin,na.rm=TRUE),digit=1))
dayreference$`Drill Title` <- factor(dayreference$`Drill Title`, levels = drill_order)

# Reorder the rows according to the factor order of `Drill Title`
dayreference <- dayreference %>%
  arrange(`Drill Title`)

my.data<-cbind(my.data,dayreference[,c(2:4)])
my.data$HMLDPercent<-100*round(my.data$HMLMin/my.data$HMLDnorm,digit=2)
my.data$AccelPercent<-100*round(my.data$AccelMin/my.data$Accelsnorm,digit=2)
my.data$VHSRPercent<-100*round(my.data$VHSRMin/my.data$VHSRnorm,digit=2)


color.picker1 <- function(z){
  if(is.na(z)){return(0)}
  else if(z <= 80){return(1)}
  else if( z > 80 & z < 120){return(2)}
  else {return(3)}
}


a<-condformat(my.data) %>%
  rule_fill_discrete(HMLMin, expression = sapply(my.data$HMLDPercent,
                                                color.picker1),colours=c("0" = "white", "1" = "navy", 
                                                                          "2" =  "lightgreen", "3" = "darkred"))
b<-a %>%rule_fill_discrete(VHSRMin, expression = sapply(my.data$VHSRPercent,
                                                          color.picker1),colours=c("0" = "white", "1" = "navy", 
                                                                                   "2" =  "lightgreen", "3" = "darkred")) 
c<-b %>%
  rule_fill_discrete(AccelMin, expression = sapply(my.data$AccelPercent,
                                                      color.picker1),colours=c("0" = "white", "1" = "navy",  "2" =  "lightgreen", "3" = "darkred")) 

c[,c(1:4)]


```


# Individual Summary 
This is a player compared to their own session average. 
```{r, echo=FALSE,message=FALSE,warning=FALSE, out.width="125%",out.height="125%"}
dayreference <- daydata %>%
  group_by(Name) %>%
  dplyr::summarize(HMLDnorm=round(mean(HMLD,na.rm=TRUE),digit=0),
                    Accelsnorm=round(mean(Accels,na.rm=TRUE),digit=0),
                    VHSRnorm=round(mean(`VHSR >70%`,na.rm=TRUE),digit=0))

my.data<-merge(trainingfull,dayreference, by="Name")
my.data$HMLDPercent<-round(100*(my.data$HMLD/my.data$HMLDnorm)-100,digit=0)
my.data$AccelPercent<-round(100*(my.data$Accels/my.data$Accelsnorm)-100,digit=0)
my.data$VHSRPercent<-round(100*(my.data$`VHSR >70%`/my.data$VHSRnorm)-100,digit=0)

my.data$VHSRPercent<-ifelse(my.data$VHSRPercent=="NaN"|my.data$VHSRPercent=="Inf",0,my.data$VHSRPercent)

my.data$AccelPercent<-ifelse(my.data$AccelPercent=="NaN"|my.data$AccelPercent=="Inf",0,my.data$AccelPercent)

my.data$HMLDPercent<-ifelse(my.data$HMLDPercent=="NaN"|my.data$HMLDPercent=="Inf",0,my.data$HMLDPercent)

 make_plot <- function(data, percent_col, value_col, y_label) {

  max_abs <- max(abs(c(min(data[[percent_col]], na.rm = TRUE),
                       max(data[[percent_col]], na.rm = TRUE))))

  # Create category with FIXED levels
  fill_cat <- cut(data[[percent_col]],
                  breaks = c(-Inf, -20, 20, Inf),
                  labels = c("low", "normal", "high"))

  fill_cat <- factor(fill_cat, levels = c("low", "normal", "high"))

  p <- ggplot(data,
              aes(x = reorder(Name, -data[[percent_col]]),
                  y = data[[percent_col]],
                  fill = fill_cat)) +

    geom_bar(stat = "summary", fun = round_mean, position = "dodge") +

    scale_fill_manual(values = c(
      "low" = "navy",
      "normal" = "lightgreen",
      "high" = "darkred"
    ), drop = FALSE) +   # 

    scale_y_continuous(labels = function(x) paste0(x, "%"),
                       limits = c(-max_abs, max_abs)) +

    xlab("") +
    ylab(y_label) +

    theme(
      legend.position = "none",
      axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1),
      text = element_text(size = 16)
    )

  ggplotly(p, tooltip = c("Name", value_col)) %>%
    layout(
      legend = list(title = NULL),
      hovermode = "closest",
      hoverlabel = list(font = list(color = "white"))
    )
}
b <- make_plot(my.data, "HMLDPercent", "HMLD", "HMLD")
b

b <- make_plot(my.data, "AccelPercent", "Accels", "Accels")
b

b <- make_plot(my.data, "VHSRPercent", "VHSR >70%", "VHSR")
b
```
